---
title: "Lab 5"
author: ""
date: ""
output: 
  html_document:
    toc: true
    number_sections: false
    toc_float: true
    df_print: paged
---

```{r include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE,
                      comment = "#>", highlight = TRUE, error = TRUE,
                      fig.align = "center")
```

## Packages

```{r}
library(tidyverse)
```

## Regex basics

In the below parts, identify the pattern to ultimately subset `x` or provide
a full match corresponding to the specified components of `x`. The only
code you need to provide is the regular expression to the `pattern` argument
in `str_detect()` or `str_match()`.

#### Letters

Find a pattern so only the first three components of `x` are subset.

```{r}
x <- c("abcde", "ab", "abc", "aa")
x[str_detect(x, pattern = "")]
```

#### Digits: `\d`

Find a pattern so all components of `x` are subset.

```{r}
x <- c("abc124ewi", "124jtk", "124")
x[str_detect(x, pattern = "")]
```

Find a pattern so all components of `x` are subset.

```{r}
x <- c("test2", "help3", "4", "a0df")
x[str_detect(x, pattern = "")]
```

#### The dot: `.`

Find a pattern so only the components of `x` with a dot are subset.

```{r}
x <- c(".png", "aei1", "first.last", "%@?.")
x[str_detect(x, pattern = "")]
```

Find a pattern so all but the last component of `x` are subset.

```{r}
x <- c("a", "\\", "b", "4", "$", "\t", "\n")
x[str_detect(x, pattern = "")]
```

#### Classes: `[ ]`

Find a pattern so only the animals are subset.

```{r}
x <- c("cat", "rat", "bat", "hat")
x[str_detect(x, pattern = "")]
```

Find a pattern so only the names are subset 
(those given with upper-case letters).

```{r}
x <- c("Shawn", "fawn", "Dawn", "pawn", "lawn", "Jon")
x[str_detect(x, pattern = "")]
```

#### Repititions: `{ }`, `*`, `+`

Find a pattern so only the incorrect spellings are subset.

```{r}
x <- c("hello", "helllo", "hellllllo", "helllllllo")
x[str_detect(x, pattern = "")]
```

Find a pattern so the first three components are matched completely. Your
result should be a 4 x 1 matrix with the value `NA` in row four.

```{r}
x <- c("aaaabcc", "aabbbbc", "aacc", "a")
str_match(x, pattern = "")
```

#### Optionality: `?`

Find a pattern to completely match the statements that contain numbers. Your
result should be a 4 x 1 matrix with the value `NA` in row three.

```{r}
x <- c("1 name available?", "2 names available?", "no names found!",
       "22 names available?")
str_match(x, pattern = "")
```

#### Anchors: `^` and `$`

Find a pattern to completely match the first statement in `x`. Your
result should be a 4 x 1 matrix with the value `NA` in rows two through four.

```{r}
x <- c("My exam was successful", "Unfortunately, My exam was unsuccessful",
       "My exam was a success", "My exam was successful today")
str_match(x, pattern = "")
```

#### Capture groups: `( )`

Find a pattern to completely match all the dates with the months as a capture
group. Your result should be a 4 x 2 matrix with the second column being
only the month abbreviations.

```{r}
x <- c("Feb 11", "Sep 21", "Nov 2020", "Jun 1995")
str_match(x, pattern = "")
```

Find a pattern to completely match all the dates with the months as a capture
group and the years as another capture group. Your result should be a 4 x 3 
matrix with the second column being only the month abbreviations and the
third column being the years.

```{r}
str_match(x, pattern = "")
```

Find a pattern to completely match all the dates with the full date as a capture
group and the years as another capture group. Your result should be a 4 x 3 
matrix with the second column being the full date and the
third column being the years.

```{r}
str_match(x, pattern = "")
```

## Regex challenges

In the below parts, identify the pattern to ultimately subset `x` or provide
a full match corresponding to the specified components of `x`. The only
code you need to provide is the regular expression to the `pattern` argument
in `str_detect()` or `str_match()`.

Find a pattern so all but the last component are matched completely. Your
result should have a value of `NA` for the last component.

```{r}
x <- c("3.14", "100", "-259.11", "2.3e3", "1,112", "720p")
str_match(x, pattern = "")[, 1]
```

Find a pattern so all the image files (`.jpg` and `.png`) are extracted with
their name and file extensions as capture groups. Your result should be an
8 x 3 matrix with rows two, three, and six not having `NA` values.

```{r}
x <- c(".gitignore", "img-01.png", "vis.jpg", ".Rhistory", "lab5.R",
       "update_vis.jpg", "lab5.html", "png.pdf")
str_match(x, pattern = "")
```

Find a pattern to completely match all the phone numbers.

```{r}
x <- c("423-114-4432", "572-525-2532", "(322)523-1000", "401 342 1983",
       "3781340100", "1 800 432 1341")
str_match(x, pattern = "")
```

